---
title: "Shiny Application and Reproducible Pitch"
author: "David del Moral"
date: "August 19, 2018"
output: ioslides_presentation
runtime: shiny
resource_files:
- server.R
- ui.R
---

## Shiny Presentation {.smaller}

This peer assessed assignment has two parts:

1. Create a Shiny application and deploy it on Rstudio's servers. 

2. Use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.


## Your Shiny Application {.smaller}

* Write a shiny application with associated supporting documentation. 
* The documentation should be thought of as whatever a user will need to get started using your application.
* Deploy the application on Rstudio's shiny server
* Share the application link by pasting it into the provided text box
* Share your server.R and ui.R code on github

## Mexican Government Acquisitions 2018 (MXP) {.smaller}

###Web Application functionality

The application shows the acquisitions performed by the Mexican goverment during 2018 through the procurement platform known as Compranet (https://compranet.funcionpublica.gob.mx/web/login.html). 

The source of the data has been obtained from https://datos.gob.mx/, the open data site of the Mexican Goverment.  

The application allows to select the amount range of the contracts awarded during 2018 though slides controls. Once selected the cost range, the data frame is filtered and a plot is updated dynamically, showing a chart with the different sort of contracts awarded through the Compranet acquisitions platform.  The size of the point corresponds to the amount of the contract awarded.

The application gives an overview of where audits could be potentially focused depending on the amounts and type of acquisition procedure applied. 

Data labels and categories have been translated to English for better understanding.

## User Interface Code {.smaller}

```{r user interface, eval=FALSE}

# ui.R
library(shiny)

ui <- fluidPage(

    titlePanel("Mexican Government Acquisitions 2018 in lMillions of Mexican Pesos(MXP)"),
    
    sliderInput("range", "Contract Amount Range:",
          min = 1, max = 1000000000,
          value = c(1000000,500000000)),
    
    plotOutput("gplot")
  )

```


## Server Side Code {.smaller}
```{r server code, eval=FALSE}

# server.R
library(shiny)
library(ggplot2)
library(dplyr)

df<- read.csv(file="Compranet_2018_UTF8.csv", header=TRUE, sep="|")

dfMXP <- subset(df, df$CURRENCY == "MXP")

server <- function(input, output) {
  
  output$gplot <- renderPlot({
    filtered <-
      dfMXP %>%
      filter(CONTRACT_AMOUNT >= input$range[1],
             CONTRACT_AMOUNT <= input$range[2]
            )
      ggplot(filtered, aes(CONTRACT_TYPE, CONTRACT_AMOUNT)) + 
      geom_point(aes(col=PROCEDURE_TYPE)) +
      xlab("Contract Type") +
      ylab("Procurement Procedure")
      })
}

```

## Application Published in shinyapps.io {.smaller}


The app is avalilable at: 

https://daviddelmoral.shinyapps.io/shinyproject/

The code can be obtained from:

The source code for ui.R and server.R files are available on the GitHub repo: 

https://github.com/ddelmoral/shinyproject



## Compranet Data Sample {.smaller}

```{r data summary 1}
df<- read.csv(file="Compranet_2018_UTF8.csv", header=TRUE, sep="|")
dfMXP <- subset(df, df$CURRENCY == "MXP")
summary(df$CONTRACT_TYPE)
summary(df$CONTRACT_AMOUNT)
summary(df$PROCEDURE_TYPE)
```


